Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-02 paper.qmd
Added langevitour for Single cell data example

@@

scaled_pbmc_data_model <- scaled_pbmc |>
  filter(type == "model") |>
  select(-type)

# # Combine with the true model for visualization
# df <- dplyr::bind_rows(scaled_pbmc_data_model |> mutate(type = "model"),
#                        scaled_pbmc_data |> mutate(type = "data"))

@@

@@

scaled_pbmc_data_model <- scaled_pbmc |>
  filter(type == "model") |>
  select(-type)

>>>>

```{r}
#| label: prep-pbmc-umap-model-proj

@@

scaled_pbmc_data_model <- scaled_pbmc |>
  filter(type == "model") |>
  select(-type)
```

```{r}
#| label: langevitour-pbmc-umap-author-proj
#| eval: false

df_model_data_pbmc_n <- bind_rows(df_b_pbmc, data_pbmc)

langevitour::langevitour(df_model_data_pbmc_n[1:(length(df_model_data_pbmc_n)-1)],
                         lineFrom = distance_df_small_edges_pbmc$from,
                         lineTo = distance_df_small_edges_pbmc$to,
                         group = factor(df_model_data_pbmc_n$type,
                                        c("data", "model")),
                         levelColors = c("#a65628", "#000000"))
```

@@

```{r}
#| label: prep-pbmc-umap-model-proj-best

@@

scaled_pbmc_data_model <- scaled_pbmc |>
  filter(type == "model") |>
  select(-type)
```

```{r}
#| label: langevitour-pbmc-umap-best-proj
#| eval: false

df_model_data_pbmc_n <- bind_rows(df_b_pbmc, data_pbmc)

langevitour::langevitour(df_model_data_pbmc_n[1:(length(df_model_data_pbmc_n)-1)],
                         lineFrom = distance_df_small_edges_pbmc$from,
                         lineTo = distance_df_small_edges_pbmc$to,
                         group = factor(df_model_data_pbmc_n$type,
                                        c("data", "model")),
                         levelColors = c("#999999", "#000000"))
```
